Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-07-28 02_paper/02_study/paper_methods.Rmd
update data & plotssss

## Materials

### Eye-Tracking Apparatus

@@

@@

##### Coding Teachers' Reaction

@@

@@

#### Rating scales

@@

For the present study, the following two questions from the interview were relevant:
1. "How disturbing did you perceive this event to be?"
2. "How confident did you feel in dealing with this event?"

>>>>

## Materials and Measures

### Eye-Tracking Data

@@

#### Teachers' visual focus of attention

Teachers' areas of interest (AOI) were identified as targets where teachers looked during the micro-teaching-unit using Tobii Pro Lab Analyzer Software Version 1.171. In the present study, general AOIs where defined as the student group, the students' nametags, the teacher material, the students' material, the board and non-instructional material in the classroom (wall, window, floor). These AOIs were coded during the manual fixation mapping process during the entire micro-teaching-unit. Additionally, the disruptive person was coded as an event-based AOI only over the duration of the disruption.

--> Only eye-tracking video recordings with 70 % and above gaze sample percentages were selected for the study to ensure that one or both eyes were detected during 70 % of the recording’s duration (Chaudhuri et al, 2022). Screenshots of the video recordings were used to define the AOI in the eye-tracking videos. The coder started manual gaze mapping when the teacher entered the classroom and ended coding when the micro-teaching-unit ended. The start and end of the micro-teaching-unit was defined by a visual and acoustical signal. The two coders who were assigned to code the eye-tracking videos student employees who studied to be teachers and received a detailed introduction to the software. The intercoder reliability was checked by double coding 20 % of the videos from the whole dataset. Double coding agreement ranged from XXX % to XXX %.

We coded each fixation using the Attention Filter in Pro Lab with the velocity threshold parameter set to 100 degrees/second instead of the default 30 degrees/second. This filter is suitable for dynamic situations to study attention without separating any eye movements. By choosing the Attention Filter typical fixations, most VOR (Vestibulo-ocular reflex), smooth pursuit eye movements, and slow saccades are classified as fixations.

The relevant fixation metrics such as number of fixations, the total duration of fixations and time to first fixation on the relevant event (disruptive person) were obtained by exporting an interval-based TSV file from the Tobii Pro Lab Analyzer Software. The total fixation duration and the time to first fixation metrics were measured in milliseconds (ms) and the number of fixation in counts as an integer. To calculate the average fixation of durations for all AOIs, we divided the total duration of fixations by the number of  fixations for each AOI.

@@

##### Teachers' Reaction to disruptions

@@

XXX

@@

#### Teachers' perception of disruption and confidence using Rating scales

@@

For the present study, the following two questions from the interview were relevant:
1. "How disruptive was this event for you?"
2. "How confident did you feel in dealing with this event?"
